---
layout: page
title: Getting Started
permalink: /getting_started/
---

Your first boosted model
========================================================

First, install and fire-up R on your computer. Within R, one needs to
install the mboost package by typing

```{r eval=FALSE}
install.packages("mboost")
```

and hitting the ENTER key. Once the package is installed, you can
load it using

```{r results: hide}
library("mboost")
```

Now all mboost functions are ready to be used, for example the mboost()
function for fitting an additive regression model to the bodyfat data 

```{r}
data("bodyfat", package = "TH.data")
 
### formula interface: additive Gaussian model with
### a non-linear step-function in `age', a linear function in `waistcirc'
### and a smooth non-linear smooth function in `hipcirc'
mod <- mboost(DEXfat ~ btree(age) + bols(waistcirc) + bbs(hipcirc),
              data = bodyfat)
```

The model can be plotted

```{r fig.width=9, fig.height=6}
layout(matrix(1:3, nc = 3, byrow = TRUE))
plot(mod, ask = FALSE, main = "formula")

```

or used for computing predictions

```{r}
summary(predict(mod))
```

which can be compared to the actual response values:

```{r fig.width=6, fig.height=6}
plot(bodyfat$DEXfat, predict(mod))
abline(a = 0, b = 1)
```
