---
layout: page
title: Publications
permalink: /publications/
---

Scholary papers describing the methodology
========================================================

```{r setup, include = FALSE, cache = FALSE}
library("RefManageR")
bib <- ReadBib("TH.bib", check = FALSE)
BibOptions(check.entries = FALSE, style = "html", cite.style = "authoryear",
           bib.style = "numeric")
```
The mboost package implements componentwise functional gradient descent
boosting, originally invented by `r Citet(bib, "Buehlmann_Yu_2003")`.
The theory and package are described in the review by
`r Citet(bib, "Buehlmann:2008:StatSci")`, an overview about the implementation
is given in `r Citet(bib, "Hothorn+Buehlmann+Kneib+Schmid+Hofner_2010")`
and `r Citet(bib, "Hothorn:2006:Bioinformatics:16940323")`. A tutorial
can be found in `r Citet(bib, "Hofner_Mayr_Robinzonov_2014")`.

Applications in survival analysis are described in
`r Citet(bib, "Hothorn:2006:Biostatistics:16344280")` and
`r Citet(bib, "Schmid+Hothorn:2008a")`.

Geoadditive models have been dealt with by 
`r Citet(bib, "Kneib+Hothorn+Tutz:2009")` and
`r Citet(bib, "Hothorn+Mueller+Schroeder_2011")` and, with special emphasis
on monotonicity constraints, by `r Citet(bib, "Hofner_Mueller_Hothorn_2011")`.

Boosted quantile regression models were introduced by
`r Citet(bib, "Fenske+Kneib+Hothorn_2011")` and later extended
to longitudinal data by `r Citet(bib, "Fenske_Fahrmeir_Hothorn_2013")`
and to the derivation of prediction intervals by
`r Citet(bib, "Mayr_Hothorn_Fenske_2012")`.

The application of P-spline base-learners was discussed by
`r Citet(bib, "Schmid+Hothorn:2008b")`. Unbiased model selection
was implemented as described by `r Citet(bib, "Hofner+Hothorn+Kneib_2011")`.
An approach to non-linear time series can be found in
`r Citet(bib, "Robinzonov_Tutz_Hothorn_2012")`.
Boosted classifiers based on a direct optimisation of the partial AUC were
introduced by `r Citet(bib, "Schmid_Hothorn_Krause_2012")`.

`r Citet(bib, "Hothorn_Kneib_Buehlmann_2014")` used componentwise array
boosting to fit a novel class of conditional transformation models; 
some simplifications are given by `r Citet(bib, "Moest_Schmid_Faschingbauer_2014")`.
In a similar spirit, `r Citet(bib, "Mayr_Fenske_Hofner_2012")` use the 
package to fit GAMLSS models.

**References**

```{r results = "asis", echo = FALSE}
PrintBibliography(bib, .opts = list(check.entries = FALSE, sorting = "ynt"))
```
